Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-16 GWLDCII.tex

To construct $I_1$ we start at vertex 1, so we set $i=1$, $j = 1$, and $I_1 = \emptyset$. 
\begin{itemize}
\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, we let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators. So $I_1 = \{1,2\}$ and propagator $q$ is removed.
\item $j = 3$: $\Prop(3) = \{p\}$, so now $I_1 = \{1,2,3\}$ and propagator $p$ is removed. The only remaining propagator in the diagram is $s$.
\item $j = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
\end{itemize}
There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, or $1235$ for short. 
%So the propagators are ordered $r,q,p,s$ with respect to $I_1$, and 
$I_1$ viewed as a function is given by
\[I_1: \cP \longrightarrow [n] : \quad I_1(r) = 1,\quad I_1(q) = 2, \quad I_1(p) = 3, \quad I_1(s) = 5.\]
Applying the algorithm for all 8 starting vertices, we obtain the sets
\[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above, as we will prove in general shortly.
\end{eg}

>>>>

To construct $I_1$ we start at vertex 1, so we set $i=1$, $j = 1$, and $I_1 = \emptyset$. 
\begin{itemize}
\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, $r$ contributes at this step: $I_1(r)=1$. We let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators, $q$ contributes at this step: $I_1(q)=1$. So $I_1 = \{1,2\}$ and propagator $q$ is removed.
\item $j = 3$: $\Prop(3) = \{p\}$, so now $I_i(p) = 3$ and $I_1 = \{1,2,3\}$. The propagator $p$ is removed. The only remaining propagator in the diagram is $s$.
\item $j = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$ with $I_1(s) = 5$.
\end{itemize}
There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, or $1235$ for short. 
%So the propagators are ordered $r,q,p,s$ with respect to $I_1$, and 
$I_1$ viewed as a function is given by
\[I_1: \cP \longrightarrow [n] : \quad I_1(r) = 1,\quad I_1(q) = 2, \quad I_1(p) = 3, \quad I_1(s) = 5.\]
Applying the algorithm for all 8 starting vertices, we obtain the sets
\[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above, as we will prove in general shortly.
\end{eg}

Notice that for each element in the Grassmann necklace, the propagators contribute in a particular order. It is sometimes useful to think of the propagators in this order. 
\begin{dfn} \label{prop order dfn}
Given a set $\cP$ of $k$ propagators defining a Wilson loop diagram $(\cP, [n])$, the Grassmann necklace element $I_i$ imposes an ordering on it $\cP^i = \{p_1 \ldots p_k\}$ where $p_m$ is the $m^{th}$ propagator to contribute to $I_i$. We write $\cP_m^i = \{p_1 \ldots p_m\}$ to be the first $m$ propagators that contribute to $I_i$. 
\end{dfn}

In the sequel, when we refer to orderings on propagators, we refer to the ordering $\cP^i$. Note that different elements of the Grassmann necklace impose different orderings on the propagators. \hlfix{{Furthermore, Lemma \ref{no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$. That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.}}{Maybe move closer to reference lemma}
